A pipeline to analyse time-course gene expression data

### 2019-05-15 scripts/manuscript.Rmd
Renaming functions, adding text, fixing FIXMEs

```{r schema, echo=FALSE, fig.width=4, fig.cap="Workflow for analyzing time-course datasets."}

@@

2) Global analysis, where we consider the expression pattern globally over
time, and consider what genes have either different patterns between
conditions or a changing pattern (i.e. non-constant) over time. A common
approach first step is to fit a spline model to each gene **FIXME add refs**,
and then use that spline model to test for different kinds of differential
expression across time.

The per-time point analysis is using classical differential expression
approaches, and is often the approach advocated when dealing with small
time-course datasets, where there are only a few time points **FIXME add
citation to edgeR/limma vignette or DESEQ2**. For long time-course datasets,
however, a separate test for each time-point results in creating many
different tests, for example one for every time point, the results of which
are difficult to integrate. We find in practice that the global analysis
simplifies analysis and of longer time courses data, with per-time point
analysis reserved for particularly interesting comparisons of individual
time-points.

@@

We start by creating the
`splines_model` object using the `create_splines_model` function.

@@

`moanin` provides a simple interface to perform a timepoint by timepoint differential
expression analysis. This is traditionally done by the user defining the comparisons (called `contrasts` in linear models).  Under the hood, simply calls `limma` [@ritchie:limma] on the set of
contrasts provided. **EAP: Can we comment on using it for RNA-Seq??**

@@

**FIXME rename the function to something better**

**EAP: And don't use 'week' in function name!**

>>>>

```{r schema, echo=FALSE, fig.width=3, fig.cap="Workflow for analyzing time-course datasets."}

@@

2) Global analysis, where we consider the expression pattern globally over
time, and consider what genes have either different patterns between
conditions or a changing pattern (i.e. non-constant) over time. A common
approach first step is to fit a spline model to each gene
[@storey:significance],
and then use that spline model to test for different kinds of differential
expression across time.

The per-time point analysis is using classical differential expression
approaches, and is often the approach advocated when dealing with small
time-course datasets, where there are only a few time points 
[@ritchie:limma, @robinson:edgeR, @love:moderated] . For long time-course datasets,
however, a separate test for each time-point results in creating many
different tests, for example one for every time point, the results of which
are difficult to integrate. We find in practice that the global analysis
simplifies analysis and of longer time courses data, with per-time point
analysis reserved for particularly interesting comparisons of individual
time-points.

@@

We start by creating the `splines_model` object using the
`create_splines_model` function. The `splines_model` object contains a number
of metadata and options used throughout this analysis: the condition and
timepoints of each samples, the formula object used or the basis or the
degrees of freedom of the model. The metadata data.frame object should
contain at least two columns: one named `Group`, containing the  treatement
effect, and a second one named `Timepoint` containing the timepoint
information.

```{r echo=FALSE}
kable(head(meta))
```

If no formula is provided, it will default to the following: 
`formula = ~Group:splines::ns(Timepoint, df=degrees_of_fredoom) + Group + 0`

@@

`moanin` provides a simple interface to perform a timepoint by timepoint differential
expression analysis. This is traditionally done by the user defining the comparisons (called `contrasts` in linear models).  Under the hood, simply calls `limma` [@ritchie:limma] on the set of
contrasts provided. By default, it expects RNA-Seq contact counts, and will
estimate voom weights. We tern

@@
